Implicit yaddayadda

### 2011-10-25 papers/PLDI2012/implicitization.tex
tableau de résultats

\JH{La comparaison DIS/G+PF n'est pas encore correcte (DIS pas compl\`etement
impl\'ement\'e)\\} 
Figures \ref{fig:techniques} shows the results of various comparisons between
the different analysis techniques.

>>>>

Figures \ref{fig:techniques} shows the results of various comparisons between
the different analysis techniques.

\begin{table*}
\begin{center}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|c|c||c|c|c||} \hline
\textbf{Benchmark} & \multicolumn{3}{c||}{\textbf{G/S}}
& \multicolumn{3}{c||}{\textbf{PF/S}}
& \multicolumn{3}{c||}{\textbf{PF/G}}
& \multicolumn{3}{c||}{\textbf{G+PF/PF}}
& \multicolumn{3}{c||}{\textbf{G+PF/G}} \\ \cline{2-16}
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} 
& \textbf{lt} & \textbf{gt} & \textbf{un} \\
 \hline
 \input{table1.tex}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focused} technique (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm. \textbf{lt} column gives the
percentage of invariants more precise with the left-side technique,
\textbf{gt} the percentage of invariants better with the right-side technique,
and \textbf{un} gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
\end{table*}
